An asymptotically normal out-of-sample test of equal predictive accuracy for nested models

### 2014-11-04 mixedwindow.tex
Revise theoretical component of paper

\author{Gray Calhoun\thanks{ Economics Department; Iowa State
    University; Ames, IA 50011.  Telephone: (515) 294-6271.  Email:
    \guillemotleft \protect\url{gcalhoun@iastate.edu}\guillemotright,
    web: \guillemotleft www.econ.iastate.edu/\textasciitilde
    gcalhoun\guillemotright.
    I'd like to
    thank Helle Bunzel, Todd Clark, Graham Elliott, Yu-Chin Hsu,
    Michael McCracken, Pablo Pincheira, Allan Timmermann, Stephane
    Meng-Feng Yen and participants at the 2011 Midwest Econometrics
    Group meeting and the 2013 \nber-\nsf\ Time Series conference
    for helpful comments and discussions.  I'd also like to thank Amit
    Goyal for providing computer code and data for his 2008
    RFS paper with Ivo Welch \citep{GoW:08}.}\\%
  Iowa State University}

@@

\noindent JEL Classification Numbers: C22, C53

@@

\section{Introduction} This paper proposes an out-of-sample (\oos)
test statistic that is asymptotically normal with mean zero even when
the models studied are nested.  This paper also proves that common
block bootstrap methods consistently estimate the statistic's
distribution, and shows how the statistic can be used to study many
models simultaneously while maintaining strong control of the
familywise error (\fwe), i.e. ensuring that the probability that the
hypothesis that the model has equal predictive ability to a benchmark
is incorrectly rejected for any of the models is no higher than a
preset level.

\oos\ tests are commonly used in International Macroeconomics,
Macroeconomics, and Finance (see, for example, \citealt{MeR:83};
\citealt{StW:03}; and \citealt{GoW:08}) and there is a substantial
literature developing the theoretical properties of these statistics,
beginning primarily with \citet{DiM:95} and
\citet{Wes:96}.%
\footnote{Other papers in this literature include
  \citet{WeM:98}, \citet{Mcc:98,Mcc:00},
  \citet{ClM:01,ClM:05-2,ClM:05,ClM:11b,ClM:12,ClM:12b},
  \citet{CCS:01}, \citet{CoS:02,CoS:04,CoS:07}, \citet{Whi:00},
  \citet{InK:04,InK:06}, \citet{Han:05}, \citet{Ros:05},
  \citet{ClW:06,ClW:07}, \citet{Ana:07}, \citet{GiR:09,GiR:10},
  \citet{HuW:10}, \citet{HLN:11}, \cite{InR:11}, \cite{Pin:11},
  \cite{RoS:11,RoS:11b}, and \citet{Cal:11}, among others.  For recent
  reviews of this literature and additional references, see
  \citet{McW:02}, \citet{CoS:06}, \citet{Wes:06}, \citet{ClM:11c},
  \citet{CoD:11}, and \citet{Gia:11}} %
In a pair of papers,
\citet{ClW:06,ClW:07} develop an \oos\ test of the null hypothesis
that a small benchmark model is correctly specified.  Their test
compares the forecasting performance of a pair of nested models, and
the null hypothesis is that the innovations in the smaller model form
a Martingale Difference Sequence (\mds).  This test procedure is popular, and
one assumes that this is due in part to the statistic's convenience,
the statistic is approximately normal after adjusting for the
estimation error of the larger model.  Normality comes from a
fixed-length rolling window, as in \citet{GiW:06}, and the adjustment
centers the statistic appropriately.  This statistic is especially
convenient because other \oos\ tests for similar hypotheses
(\citealt{CCS:01}; \citealt{ClM:01,ClM:05}; \citealt{CoS:02,CoS:04};
and \citealt{Mcc:07}; among others) have a nonstandard limit
distribution and place restrictions on the models under consideration,
while other asymptotically normal statistics test a different null
hypothesis \citep{GiW:06} or place assumptions on the models and \dgp\
that are often violated in empirical work (\citealt{DiM:95};
\citealt{Wes:96}; \citealt{WeM:98};
\citealt{Mcc:00}).%
\footnote{\citet{DiM:95} assume that the models are
  not estimated. \citet{Wes:96}, \citet{WeM:98}, and \citet{Mcc:00}
  implicitly assume that the models do not converge to the same limit,
  which rules out nesting.} %

@@

In this paper, I show that a modified version of their statistic is
asymptotically normal even when the smaller model is estimated.  To
achieve normality, the pseudotrue benchmark model must be estimated
consistently, but the larger alternative model must continue to be
estimated inconsistently so that the test statistic is not degenerate
when the models are nested. We can meet both needs by
using different window strategies for each model: the benchmark model
is estimated using a recursive window and the alternative with a
fixed-length rolling window.

Mixing window strategies is uncommon but needn't be. In most
applications, the null hypothesis imposes stability as well as equal
accuracy between the two models.  The benchmark model rarely allows
for breaks, parameter drift, or other forms of
instability,%
\footnote{Exceptions are \citepos{StW:07}
  \allcaps{IMA}(1,1) and \allcaps{UC}-\allcaps{SV} models of inflation.} %
but the
researcher is typically concerned about instability.  Indeed, concern
about instability is often given as a reason for doing an \oos\
analysis, especially with a short rolling window.%
\footnote{This
  motivation is discussed by \citet{StW:03}, \citet{PeT:05,PeT:07},
  \cite{GiW:06}, \citet{GoW:08}, \citet{ClM:09c}, and
  \cite{GiR:09,GiR:10}, among others.} %
A researcher could impose
stability on both models by using a recursive window or relax
stability for both by using a rolling window; either approach should
not affect the test's size, but may affect power.  But the researcher
could instead impose stability on the benchmark and relax it for the
alternative by using a recursive window for the benchmark and a
rolling window for the alternative model.  This approach could have a
power advantage and is similar in spirit to using a Likelihood Ratio
Test instead of an \lm\ or Wald test, which depend on just the
restricted or unrestricted model respectively.

This paper's statistic has a substantial advantage over existing \oos\
tests for nested models: the alternative can be essentially arbitrary
as long as high level moment conditions hold.  In particular,
researchers can use model selection techniques like the \aic\ or \bic\
to determine the number of lags to include, the particular exogenous
variables to include, etc.  Other methods that test a similar
hypothesis are unable to handle these models \citep[except][which does
not allow the benchmark to be estimated]{ClW:06}; \citet{GiW:06} are
able to handle such models for both the alternative and the benchmark
but, as mentioned earlier, they test a different aspect of forecasting
performance.

This paper focuses on nested models, as they have received the most
attention in the empirical and theoretical literature, but the
statistic can be used with non-nested models as well.  This generality
is useful, since \citepos{Wes:96} results do not apply to non-nested
models if they both encompass the true \dgp,%
\footnote{\citet{ClM:11b}
  call this scenario, ``overlapping models.''} %
which is allowable
under the null: in the limit, both models will converge to the \dgp\
and give identical forecasts.  Consequently, the naive \oos\ $t$-test
is invalid, even after correcting the standard error if necessary to
reflect parameter uncertainty.  \citet{ClM:11b} show that the fixed
window \oos\ $t$-test remains normal for these models but the
recursive and rolling windows (with the window size increasing to
$\infty$) do not, and provide a procedure for pointwise (but not
uniformly) valid tests for the recursive and rolling windows and
uniformly valid tests for the fixed window.  The test proposed in this
paper is uniformly valid and places fewer assumptions on the models
under study and the true \dgp.

The next section presents our new statistic. Section~\ref{sec:2} presents
simulations that compare our pairwise \oos\ test to \poscw\ original
statistics. Section~\ref{sec:3} demonstrates the use of our statistic
by reanalyzing \citepos{GoW:08} study of excess return
predictability and Section~\ref{sec:4} concludes. Proofs of
our results have been put in a separate Appendix along with
some minor supporting arguments \citep{Cal:14}.

@@

Suppose for now that a researcher is interested in
predicting the target variable $y_{t+1}$ with a vector of regressors
$x_t$; also let $v_t$ be another random process that is believed to
potentially contain information about $y_{t+1}$ and suppose that
$(y_t, x_t, v_t)$ is stationary and weakly dependent.
In addition,
let $\btrue = (\E x_t x_t')^{-1} \E x_t y_{t+1}$ be the pseudotrue
coefficient for the regression of $y_{t+1}$ on $x_t$ and define
$\ep_{t+1} = y_{t+1} - x_t'\btrue$.  If this linear model is
correctly specified, then $\ep_{t+1}$ is an \mds\ with respect
to the information set
\begin{equation*}
\mathcal{F}_t \equiv \sigma((x_t, v_t, y_t), (x_{t-1}, v_{t-1},
y_{t-1}),\dots),
\end{equation*}
and we can see immediately that
\begin{equation}
  \label{eq:4}
  \oclt{t} \ep_{t+1} (v_t - x_t'\btrue)
\end{equation}
obeys an \mds\ \clt and is asymptotically normal as $P \to \infty$,%
\footnote{This claim assumes that the asymptotic variance of the
  sample average is uniformly positive, a requirement that we will
  address in Section~\ref{sec:1b}.} %
with $R$ an arbitrary starting value%
\footnote{It will be clear momentarily why the summation begins at
  $R+1$ instead of $1$.} %
and $P = T - R$.%
\footnote{Section~\ref{sec:1b} discusses conditions under which the
  \mds\ condition holds. We will also present results that allow
  $\ep_{t+1}$ to be serially correlated.} %
Straightforward algebra \citep{ClW:07} shows that
\begin{equation}
  \label{eq:5}
  \tfrac{1}{\sqrt{P}} \osum{t} \ep_{t+1} (v_t -
  x_t'\btrue) = \tfrac{1}{2 \sqrt{P}} \osum{t} \Big[(y_{t+1} -
  x_t\btrue)^2 - (y_{t+1} - v_t)^2 + (x_t'\btrue - v_t)^2 \Big].
\end{equation}

\citet{ClW:06,ClW:07} base their \oos\ statistics on the RHS of
Equation~\eqref{eq:5}, but use a second forecast of $y_{t+1}$ as
$v_t$. (Call it $\yh_{1,t+1}$.) They use a rolling window of length
$R$ to estimate $\yh_{t+1}$%
\footnote{Making $\yh_{t+1}$ a function of $y_t, x_{t-1}, z_{t-1}
\dots, y_{t-R+1}, x_{t-R}$ and $z_{t-R}$, where $z_t$ is another weakly
dependent random process} %
and $R$ is kept finite as $T \to \infty$ so that
$\yh_{t+1}$ inherits the weak dependence properties of the
variables used to estimate it. Using a finite window length $R$ prevents
the degeneracy that can arise when comparing nested models out-of-sample (see
\citealp{ClM:01}, and \citealp{Mcc:07}), so the conditional variance
of the \oos\ average remains positive and the average obeys a \clt.%
\footnote{This approach was first introduced by \citet{GiW:06}.} %

\citet{ClW:06,ClW:07} develop a test of whether $\ep_{t+1}$ is
an \mds. In the 2006 paper, Clark and West assume that the
coefficients on the benchmark model, $\btrue$, are zero under the null, making
$\ep_{t+1}$ observed directly. This restriction is relaxed in
the 2007 paper, where $\btrue$ is unknown and estimated with length-$R$
rolling window. Now the estimated linear model's prediction errors,
$\eph_{t+1}$, replace $\ep_{t+1}$ in the \oos\
test statistic. Unfortunately, $\eph_{t+1}$ is not an
\mds\ even when $\ep_{t+1}$ is, so the statistic is no longer
asymptotically mean-zero normal, even though this approximation
performs well in simulations. Since the window length is finite,
the estimators of $\btrue$ do not converge to $\btrue$.

This paper proposes using the same basic \oos\ statistic,
but using a recursive window to estimate $\btrue$ and produce
$\eph_{t+1}$; i.e.
\begin{equation}
  \label{eq:8}
  \bh_t = \Big(\sum_{s=2}^{t} x_{t-1} x_{t-1}'\Big)^{-1}
  \sum_{s=2}^t x_{t-1} y_t.
\end{equation}
\citepos{Wes:96} Theorem 4.1 implies that
\begin{equation*}
  \oclt{t} \Big[(y_{t+1} -
  x_t\bh_t)^2 - (y_{t+1} - v_t)^2 + (x_t'\bh_t - v_t)^2 \Big]
\end{equation*}
is asymptotically normal with mean zero under Clark and West's
\mds\ null for fairly
arbitrary processes $v_t$, as long as $v_t$ is weakly dependent and
the \oos\ statistic has uniformly positive variance.  Just as in
\citet{ClW:06,ClW:07}, these conditions are ensured if $v_t$ is
another forecast of $y_{t+1}$ based on a fixed-length rolling window.

This overview has presented an especially simple version of the result
to make the intuition as clear as possible. The next section lists the
specific assumptions for a more general case.

@@

Consider the following environment. There is a single linear
benchmark model of the target variable, $y_{t+1}$:
\begin{equation}\label{eq:1}
  y_{t+1} = x_t'\beta + \ep_{t+1}, \quad t = 1,\dots,T+1
\end{equation}
where $\beta$ is an unknown $k$-vector of parameters and $x_t$ is an
observed vector of predictors. The parameter $\beta$ is
estimated with \ols\ using a recursive window as described by
Equation~\eqref{eq:8}
and the period-$t$ forecast is given by
\begin{equation}\label{eq:3}
  \yh_{0,t+1} = x_t'\bh_t.
\end{equation}

We deviate slightly from the previous section's introduction by
allowing for multiple alternative models, as in \cite{HuW:10}. This
allowance is crucial if we want the statistic to be empirically
useful, since almost every empirical analysis considers several
alternative models at once.  Each of these alternative models is
denoted $\yh_{j,t+1}$, for $j = 1,\dots,J$, and is estiatmed with a
rolling window of length $R$.

These conditions are summarized in the first assumption.

\begin{asmp}\label{a1}%
  The benchmark forecast, $\yh_{0,t+1}$, is generated by
  Equation~\eqref{eq:3}, where $\bh_t$ is constructed with a recursive
  window and satisfies~\eqref{eq:8}. The alternative forecasts are
  estimated using a rolling window of length $R$, so $\yh_{j,t+1} =
  \psi_j(y_t,z_t,\dots,y_{t-R+1}, z_{t-R+1})$ where $\psi_j$ is a
  known function and $z_t$ is a sequence of predictors that may
  include $x_t$. The window length, $R$, remains finite as $T \to
  \infty$.
\end{asmp}

Assumption~\ref{a3} describes the \dgp. The weak dependence and moment
conditions are standard. These assumptions are slightly weaker than
similar assumptions in \citet{Wes:96} and \citet{Mcc:00}, but only
because we make use of more recent developments in limit theory, in
particular the \clt\ for Near-Epoch Dependent (\ned) processes proven by
\cite{Jon:97}.

\begin{asmp}\label{a3}%
  The series $y_t$, $x_t$, and $z_t$ are $L_2$-\ned\ of size
  $-(r-1)/(r-2)$ for $r > 2$ on either a strong mixing process of size
  $-r/(r-2)$ or a uniform mixing process of size
  $-r/(2r-2)$. Moreover, $y_t$, $x_t$, and $\yh_{j,t}$, $j =
  1,\dots,J$, have uniformly bounded $2 r$ moments.
\end{asmp}

The requirement that the alternative forecasts satisfy a moment
condition, rather than the underlying predictors $z_t$, is somewhat
unappealing but necessary. The functions $\psi_j$ that generate these
forecasts is essentially unrestricted, so even well-behaved predictors
could produce arbitrarily badly-behaved forecasts. For example, if
\begin{equation*}
  z_t \sim \iid~\bernoulli(1/2),
\end{equation*}
setting $\psi_1(y_t, z_t) = 1/z_t$ would prevent a \clt\ from holding
since the forecast equals positive infinity with probability $1/2$. It
is easy to construct less obvious examples of problematic functions as
well. Assumption~\ref{a3} implicitly rules out these functional forms
by imposing moment conditions on the alternative models' forecasts.

Finally, we define some notation for the \oos\ statistic. The
adjusted \oos\ loss for each alternative model and a hypothetical value
of $\beta$ is denoted by
\begin{equation}
  f_{jt}(\beta) = (y_{t+1} - x_t'\beta)^2
  - (y_{t+1} - \yh_{j,t+1})^2 + (x_t'\beta - \yh_{j,t+1})^2
\end{equation}
and $f_t(\beta)$ denotes the vector $(f_{1t}(\beta),\dots,f_{Jt}(\beta))$.
Also define
\begin{align*}
  \fh_t &= f_t(\bh),
  &\fb(\beta) &= \oavg{t} f_t(\beta),
  &\text{and}&
  &\fb &= \tfrac1P \sum_{t=R+1}^{T} \fh_t
\end{align*}
with $P = T - R$, and let $\Sigma$ be the asymptotic variance of
$\fb$, $\Sigma = \lim_{T \to \infty} \var(\sqrt{P} \fb)$.
Also define $\btrue$ to be the pseudotrue value of
$\beta$ that minimizes the MSE of the benchmark model,
\begin{equation*}
  \btrue = \plim \Big( \sum_{t=1}^T x_t x_t' \Big)^{-1} \sum_{t=1}^T x_t y_{t+1},
\end{equation*}
and define $f_t = f_t(\btrue)$ and $\fb^* = \fb(\btrue)$.
The next assumption ensures that $\Sigma$ is positive definite.
\begin{asmp}\label{a4}%
  The asymptotic variance of $\fb$, $\Sigma$, is positive definite.
\end{asmp}

This assumption is much less restrictive than in \cite{Wes:96}.  As in
\cite{GiW:06} and \citet{ClW:06,ClW:07}, the assumption only serves to
rule out pathological cases---for example, letting both the benchmark
and the alternative models be perfectly correlated white noise. In
\citet{Wes:96}, this assumption is a restriction on the \dgp\ as well
as the forecasting models, but in this paper it is a restriction only
on the models.

@@

Asymptotic normality of the \oos\ average follows directly from the
previous three assumptions without any other conditions. The proof is
presented in the Appendix and follows \citet{Wes:96} directly.

\begin{thm}\label{res:1}\input{mixedwindow_thm1}\end{thm}
In Theorem~\ref{res:1}, define the variables
$\gh_t = \Fh \Bh x_t(y_{t+1} - x_t'\bh_t)$,
$g_t = F B x_t (y_{t+1} - x_t'\btrue)$,
$\gb = \oavg{t} \gh_t$, and $\gb^* = \oavg{t} g_t$.

Null hypothesis: $y_{t+1} - x_t'\btrue$ is an \mds\ with respect to
\begin{equation*}
  \Fs = \sigma((x_t, y_t, z_t), (x_{t-1}, y_{t-1}, z_{t-1}), \dots).
\end{equation*}

Clearly, the main use of this theorem is to test the null hypothesis
$\E f_t = 0$.

The following remarks are relevant to Theorem~\ref{res:1}:

\begin{rem}
  Forecasters are usually interested in the one-sided alternative that
  $\E f_t > 0$; i.e. that the alternative model is expected
  to forecast better than the benchmark.
\end{rem}

>>>>

\author{Gray Calhoun\thanks{ Economics Department; Iowa State
    University; Ames, IA 50011.  Telephone: (515) 294-6271.  Email:
    \guillemotleft \protect\url{gcalhoun@iastate.edu}\guillemotright,
    web: \guillemotleft www.econ.iastate.edu/\textasciitilde
    gcalhoun\guillemotright.
    I'd like to
    thank Helle Bunzel, Todd Clark, Graham Elliott, Yu-Chin Hsu,
    Michael McCracken, Pablo Pincheira, Allan Timmermann, Ken West, Stephane
    Meng-Feng Yen and participants at the 2011 Midwest Econometrics
    Group meeting and the 2013 \nber-\nsf\ Time Series conference
    for helpful comments and discussions.  I'd also like to thank Amit
    Goyal for providing computer code and data for his 2008
    RFS paper with Ivo Welch \citep{GoW:08}.}\\%
  Iowa State University}

@@

\noindent \allcaps{JEL} Classification Numbers: C22, C53

@@

\section{Introduction}

This paper proposes an out-of-sample (\oos) test statistic that is
asymptotically normal and correctly centered even when the models
studied are nested. The test is based on one proposed by
\citet{ClW:06,ClW:07}, but we propose estimating the benchmark model
with a recursive window and the alternative models with a fixed length
rolling window. The rolling window ensures asymptotic normality, as in
\citet{GiW:06}, and the recursive window allows the null hypothesis to
be a statement about the specification of the Data Generating Process,
which is the focus of the vast majority of the \oos\ testing
literature.%
\footnote{In particular, this is the focus of \citet{Wes:96},
  \citet{ClM:01}, \citet{Mcc:07}, \citet{ClW:06}, \citet{ClW:07}, and
  many others but not \citet{GiW:06}. See \citet{Wes:06} and
  \citet{ClM:13} for a thorough overview of this literature.} %
This combination of estimation windows also gives our test statistic
high power against alternative \dgp s that cause the benchmark model
to be unstable --- structural breaks, time-varying coefficients, or
forms of nonlinearity, for example --- which is a common motivation
for using these tests.

\oos\ tests are common in International Macroeconomics,
Macroeconomics, and Finance (see, for example, \citealt{MeR:83};
\citealt{StW:03}; and \citealt{GoW:08}) and there is a substantial
literature developing the theoretical properties of these statistics,
beginning primarily with \citet{DiM:95} and
\citet{Wes:96}.
In a pair of papers,
\citet{ClW:06,ClW:07} develop an \oos\ test of the null hypothesis
that a small benchmark model is correctly specified.  Their test
compares the forecasting performance of a pair of nested models, and
the null hypothesis is that the innovations in the smaller model form
a Martingale Difference Sequence (\mds).  This test procedure is popular, and
one assumes that this is due in part to the statistic's convenience,
the statistic is approximately normal after adjusting for the
estimation error of the larger model.  Normality comes from a
fixed-length rolling window, as in \citet{GiW:06}, and the adjustment
centers the statistic appropriately.  This statistic is especially
convenient because other \oos\ tests for similar hypotheses
(\citealt{CCS:01}; \citealt{ClM:01,ClM:05}; \citealt{CoS:02,CoS:04};
and \citealt{Mcc:07}; among others) have a nonstandard limit
distribution and place restrictions on the models under consideration,
while other asymptotically normal statistics test a different null
hypothesis \citep{GiW:06} or place assumptions on the models and \dgp\
that are often violated in empirical work (\citealt{DiM:95};
\citealt{Wes:96}; \citealt{WeM:98};
\citealt{Mcc:00}).%
\footnote{\citet{DiM:95} assume that the models are
  not estimated. \citet{Wes:96}, \citet{WeM:98}, and \citet{Mcc:00}
  implicitly assume that the models do not converge to the same limit,
  which rules out nesting.} %

@@

This paper shows that a modified version of their statistic is
asymptotically normal even when the smaller model is estimated.  To
achieve normality, the pseudotrue benchmark model must be estimated
consistently, but the larger alternative model must continue to be
estimated inconsistently so that the test statistic is not degenerate
when the models are nested. We can meet both needs by
using different window strategies for each model: the benchmark model
is estimated using a recursive window and the alternative with a
fixed-length rolling window.
This approach has the further advantage over existing \oos\ tests for
nested models that the alternative can be essentially arbitrary as
long as high level moment conditions hold. In particular, researchers
can use model selection techniques like the \aic\ or \bic\ to
determine the number of lags to include, the particular exogenous
variables to include, etc. Moreover, although we focus on nested
models in this paper, the approach can be used with non-nested models
as well. As \citet{ClM:11b} have recently pointed out,
\citepos{Wes:96} results do not hold when the true \dgp\ is nested by
the benchmark and alternative models, which is allowable under the
null. (\citealp{ClM:11b}, call this scenario ``overlapping models.'')

The next section presents the intuition and theory for our new statistic.
Section~\ref{sec:2} presents
simulations that compare our pairwise \oos\ test to \poscw\ original
statistics and Section~\ref{sec:3} demonstrates the use of our statistic
by reanalyzing \citepos{GoW:08} study of excess return
predictability and Section~\ref{sec:4} concludes. Proofs of
our results have been put in a separate Appendix along with
some supporting results \citep{Cal:14b}.

@@

Suppose for now that a researcher is interested in
predicting the target variable $y_{t+1}$ with a vector of regressors
$x_t$, that $v_t$ is another random process that is believed to
potentially contain information about $y_{t+1}$, and that
$(y_t, x_t, v_t)$ is stationary and weakly dependent.
In addition,
let $\btrue = (\E x_t x_t')^{-1} \E x_t y_{t+1}$ be the pseudotrue
coefficient for the regression of $y_{t+1}$ on $x_t$ and define
$\ep_{t+1} = y_{t+1} - x_t'\btrue$.  If this linear model is
correctly specified, then $\ep_{t+1}$ is an \mds\ with respect
to the information set
\begin{equation*}
\mathcal{F}_t \equiv \sigma((x_t, v_t, y_t), (x_{t-1}, v_{t-1},
y_{t-1}),\dots),
\end{equation*}
and we can see immediately that
\begin{equation}
  \label{eq:4}
  \oclt{t} \ep_{t+1} (v_t - x_t'\btrue)
\end{equation}
obeys an \mds\ \clt\ and is asymptotically normal as $P \to \infty$,%
\footnote{This claim assumes that the asymptotic variance of the
  sample average is uniformly positive, a requirement that we will
  address in Section~\ref{sec:1b}.} %
with $R$ an arbitrary starting value
and $P = T - R$.
Straightforward algebra \citep{ClW:07} shows that
\begin{equation}
  \label{eq:5}
  \tfrac{1}{\sqrt{P}} \osum{t} \ep_{t+1} (v_t -
  x_t'\btrue) = \tfrac{1}{2 \sqrt{P}} \osum{t} \Big[(y_{t+1} -
  x_t\btrue)^2 - (y_{t+1} - v_t)^2 + (x_t'\btrue - v_t)^2 \Big]
\end{equation}
almost surely.

\citet{ClW:06,ClW:07} base their \oos\ statistics on the RHS of
Equation~\eqref{eq:5}, but use a second forecast of $y_{t+1}$ as
$v_t$. (Call it $\yh_{t+1}$.) They use a rolling window of length
$R$ to estimate $\yh_{t+1}$%
\footnote{Making $\yh_{t+1}$ a function of $y_t, x_{t-1}, z_{t-1}
\dots, y_{t-R+1}, x_{t-R}$ and $z_{t-R}$, where $z_t$ is another weakly
dependent random process} %
and $R$ is kept finite as $T \to \infty$ so that
$\yh_{t+1}$ inherits the weak dependence properties of the
variables used to estimate it. Using a finite window length $R$ prevents
the degeneracy that can arise when comparing nested models out-of-sample (see
\citealp{ClM:01}, and \citealp{Mcc:07}), so the conditional variance
of the \oos\ average remains positive and the average obeys a \clt.%
\footnote{This approach was first introduced by \citet{GiW:06}.} %

\citet{ClW:06,ClW:07} develop a test of whether $\ep_{t+1}$ is
an \mds. In their 2006 paper, Clark and West assume that the
coefficients on the benchmark model, $\btrue$, are zero under the null, making
$\ep_{t+1}$ observed directly. This restriction is relaxed in
their 2007 paper, where $\btrue$ is unknown and estimated with length-$R$
rolling window. Now the estimated linear model's prediction errors,
$\eph_{t+1}$, replace $\ep_{t+1}$ in the \oos\
test statistic. Unfortunately, $\eph_{t+1}$ is not an
\mds\ even when $\ep_{t+1}$ is, so the statistic is no longer
asymptotically mean-zero normal, even though this approximation
performs well in simulations. Since the window length is finite,
the estimators of $\btrue$ do not converge to $\btrue$.

This paper proposes using the same basic \oos\ statistic,
but using a recursive window to estimate $\btrue$ and produce
$\eph_{t+1}$:
\begin{align}
  \label{eq:8}
  \bh_t &= \Big(\sum_{s=1}^{t-1} x_{s} x_{s}'\Big)^{-1}
  \sum_{s=1}^{t-1} x_{s} y_{s+1}
  && \text{and}
  &
  \eph_{t+1} &= y_{t+1} - x_t'\bh_t
\end{align}
for each $t$.
\citepos{Wes:96} Theorem 4.1 implies that
\begin{equation*}
  \oclt{t} \Big[(y_{t+1} -
  x_t\bh_t)^2 - (y_{t+1} - v_t)^2 + (x_t'\bh_t - v_t)^2 \Big]
\end{equation*}
is asymptotically normal with mean zero under Clark and West's
\mds\ null for fairly
arbitrary processes $v_t$, as long as $v_t$ is weakly dependent and
the \oos\ statistic has uniformly positive variance.  Just as in
\citet{ClW:06,ClW:07}, these conditions are ensured if $v_t$ is
another forecast of $y_{t+1}$ based on a fixed-length rolling window.

This overview has presented an especially simple version of the result
to make the intuition as clear as possible. The next section lists the
specific assumptions for the more general case.

@@

Consider the following environment. There is a single linear
benchmark model of the target variable, $y_{t+1}$:
\begin{equation}\label{eq:1}
  y_{t+1} = x_t'\beta + \ep_{t+1}, \quad t = 1,\dots,T+1
\end{equation}
where $\beta$ is an unknown $k$-vector of parameters and $x_t$ is an
observed vector of predictors. The parameter $\beta$ is estimated with
\ols\ using a recursive window as described by Equation~\eqref{eq:8}.
The alternative model is denoted $\yh_{1,t+1}$ and is estimated with a
rolling window of length $R$.

The main conditions on the \dgp\ are summarized in the first
assumption.  The weak dependence and moment conditions are
standard. These assumptions are slightly weaker than similar
assumptions in \citet{Wes:96} and \citet{Mcc:00}, but only because we
make use of more recent developments in limit theory, in particular
the \clt\ for Near-Epoch Dependent (\ned) processes proven by
\cite{Jon:97} and the \fclt\ of \cite{JoD:00b}.

\begin{asmp}\label{a1}%
  The data are generated by the relationship
  \begin{equation}
    y_{t+1} = x_t'\btrue + \ep_{t+1}
  \end{equation}
  for $t=1,2,\dots$, for some value $\btrue$, with $\E x_t \ep_{t+1} =
  0$, $\E \ep_{t+1}^2 > 0$, and $\E x_t x_t'$ positive definite for
  all $t$. Also assume that there is an additional sequence of random
  vectors $z_t$ and the processes $\ep_{t+1}$, $x_t$, and $z_t$ are
  $L_2$-\ned\ of size $-(r-1)/(r-2)$ for $r > 2$ on either a strong
  mixing process of size $-r/(r-2)$ or a uniform mixing process of
  size $-r/(2r-2)$.
\end{asmp}

The next assumption defines the forecasting models and adds additional
constraints to the \dgp.

\begin{asmp}\label{a3}%
  The benchmark forecast is $x_t'\bh_t$, where $\bh_t$ is constructed
  with a recursive window according to~\eqref{eq:8}; the partial sums
  $\sum_{s=1}^{t-1} x_s x_s' / (t-1)$ are almost surely invertible for
  all $t \geq R$ (uniformly in $T$).  The alternative forecast
  satisfies
  \begin{equation}
    \yh_{1,t+1} = \psi(y_t,z_t,\dots,y_{t-R+1}, z_{t-R+1})
  \end{equation}
  where $\psi$ is a known measurable function and the window length,
  $R$, remains finite as $T \to \infty$. Moreover, the vector
  $(\ep_{t+1}, x_t, \yh_{t+1})$ has uniformly bounded $2 r$ moments and is
  4th order stationary.
\end{asmp}

The requirement that the alternative forecast satisfies moment
conditions, rather than the underlying predictors $z_t$, is somewhat
unappealing but necessary. The function $\psi$ that generates these
forecasts is otherwise nearly unrestricted, so even well-behaved predictors
could produce arbitrarily badly-behaved forecasts. For example, if
\begin{equation*}
  z_t \sim \iid~\bernoulli(1/2),
\end{equation*}
setting $\psi(y_t, z_t) = 1/z_t$ would prevent a \clt\ from holding
since the forecast equals positive infinity with probability $1/2$. It
is easy to construct less obvious examples of problematic functions as
well. Assumption~\ref{a3} implicitly rules out these functional forms
by imposing moment conditions on the alternative models' forecasts.

Our next assumption ensures that the asymptotic variance of the \oos\
average is positive.
\begin{asmp}\label{a4}%
  The asymptotic variance-covariance matrix
  \begin{equation}
    \var \Bigg(
      \oclt{t} \begin{pmatrix} x_t \\ \yh_{t+1} \end{pmatrix} \ep_{t+1}
      \Bigg)
  \end{equation}
  is uniformly positive definite (in $T$).
\end{asmp}
This assumption is much less restrictive than in \cite{Wes:96}.  As in
\cite{GiW:06} and \citet{ClW:06,ClW:07}, the assumption only serves to
rule out pathological cases --- for example, letting the alternative
model consist of only the first regressor of the benchmark. In \citet{Wes:96}, this
assumption is a restriction on the \dgp\ as well as the forecasting
models, but in this paper it is a restriction only on the models.

The last assumption restricts the class of \hac\ variance estimators
we will consider. We use the same class of estimators studied by
\citet{JoD:00} (their class $\mathcal{K}$); see their paper for
further discussion.
\begin{asmp}\label{a5}%
  $K$ is a function from $\Re$ to $[-1,1]$ such that $K(0) = 1$, $K(x)
  = K(-x)$ for all $x$, $K(\cdot)$ is continuous at zero and all but a
  finite number of points, and
  \begin{gather*}
    \int_{-\infty}^{\infty} \lvert K(x) \rvert\, dx < \infty,
    \intertext{and}
    \int_{-\infty}^{\infty} \Bigg\lvert
    \int_{-\infty}^{\infty} K(z) e^{ixz}\,dz \Bigg\rvert\, dx < \infty.
  \end{gather*}
\end{asmp}

Last, we define some notation that will be used to derive the
theoretical properties of our \oos\ statistics.  The information set
that contains the information available for forecasting $y_{t+1}$ is
\begin{equation*}
  \Fs_t = \sigma(y_t, x_{t+1}, z_{t+1}, y_{t-1}, x_t, z_t,\dots).
\end{equation*}
The adjusted \oos\ loss for the alternative model using a hypothetical
value of $\beta$ to produce the benchmark forecast is denoted by
\begin{equation*}
  f_t(\beta) = (y_{t+1} - x_t'\beta)^2 - (y_{t+1} - \yh_{t+1})^2 + (x_t'\beta - \yh_{t+1})^2.
\end{equation*}
Define the additional terms $\fh_t = f_t(\bh_t)$, $f_t = f_t(\btrue)$,
\begin{gather*}
  \gh_t = \Bigg[\oavg{s} (4 x_s'\bh_s - 2 y_{s+1} - 2 \yh_{s+1}) x_s'\Bigg]\,
          \Bigg[\tfrac{1}{T-1} \sum_{s=1}^{T-1} x_s x_s'\Bigg]^{-1} x_t \eph_{t+1}
  \intertext{and}
  g_t = \E\Big[(4 x_t'\beta - 2 y_{t+1} - 2 \yh_{t+1}) x_t'\Big] \, (\E x_t x_t')^{-1} x_t \ep_{t+1}
\end{gather*}
and the \oos\ averages $\fb = \osum{t} \fh_t/P$, $\fb^* = \osum{t} f_t/P$,
$\fb = \osum{t} \gh_t/P$, and $\gb^* = \osum{t} g_t/P$.

@@

Asymptotic normality of the \oos\ average now follows directly from the
first three assumptions without other conditions. The proof is
presented in the Appendix and follows \citet{Wes:96} closely.

\begin{thm}\label{res:1}\input{mixedwindow_thm1}\end{thm}
